Appendix S1 - \emph{Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models}

### 2020-12-02 analysis/paper/appendix/appendix_s1.Rmd
made the font size 10 in all tables in main document and appendix

if (doc.type != "docx") {
mine_tab_df %>%
  select(-selected) %>%
  kable(digits = 3,
        booktabs = T,
        longtable = T,
        caption = 'MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.') %>%
  kable_styling(fixed_thead = T,
                latex_options = c('repeat_header',
                                  'scale_down',
                                  'HOLD_position')) %>%
  row_spec(row = which(mine_tab_df$selected),
           bold = T) %>%
  column_spec(2, width = "2in") %>%
  column_spec(3, width = "1in") %>%
  column_spec(c(4:6), width = "0.5in")
}

if(doc.type == 'docx') {
  library(pander)
  mine_tab_df %>%
    select(-selected) %>%
    pander(digits = 3,
           caption = '(\\#tab:mic-tab)MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.',
           emphasize.strong.rows = which(mine_tab_df$selected),
           split.tables = Inf)
}

@@

if (doc.type == "latex") {
  corrr_df %>%
    kable(digits = 2,
          booktabs = T,
          longtable = T,
          format = "latex",
          caption = "Pearson correlation coefficient between each variable within a habitat category.") %>%
    kable_styling(fixed_thead = T,
                  latex_options = c('repeat_header',
                                    'scale_down',
                                    'HOLD_position')) %>%
    row_spec(new_catg_rows,
             hline_after = T) %>%
    column_spec(1, width = "1in") %>%
    column_spec(c(2, 3), width = "2in")
}

if (doc.type == "html") {
  corrr_df %>%
    kable(digits = 2,
          booktabs = T,
          # longtable = T,
          caption = "Pearson correlation coefficient between each variable within a habitat category.") %>%
    kable_styling(fixed_thead = T,
                  latex_options = c('repeat_header',
                                    'scale_down',
                                    'HOLD_position')) %>%
    collapse_rows(columns = 1,
                  latex_hline = "major",
                  valign = "top")
}

if(doc.type == 'docx') {
  library(pander)

  corrr_df %>%
    pander(digits = 2,
           caption = "(\\#tab:corr-tab)Pearson correlation coefficient between each variable within a habitat category.",
           split.tables = Inf)

>>>>

if(doc.type != "docx") {
  mine_tab_df %>%
    select(-selected) %>%
    mutate(Category = recode(Category,
                             "ChannelUnit" = "Channel Unit",
                             "SideChannel" = "Side Channel")) %>%
  kable(digits = 3,
        booktabs = T,
        longtable = T,
        caption = 'MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.') %>%
    kable_styling(fixed_thead = T,
                  font_size = 10,
                  latex_options = c('repeat_header',
                                    'scale_down',
                                    'HOLD_position')) %>%
    row_spec(row = which(mine_tab_df$selected),
             bold = T) %>%
    column_spec(2, width = "2in") %>%
    column_spec(3, width = "1in") %>%
    column_spec(c(4:6), width = "0.5in")
}

if(doc.type == 'docx') {
  library(pander)
  panderOptions("graph.fontsize", 10)
  mine_tab_df %>%
    select(-selected) %>%
    pander(digits = 3,
           caption = '(\\#tab:mic-tab)MIC statistic for top metrics within each habitat category, sorted by category and MIC value. The percent of records for which each habitat metric measurement was missing or zero is also shown. Metrics selected for the QRF model are in bold.',
           emphasize.strong.rows = which(mine_tab_df$selected),
           split.tables = Inf)
}

@@

if (doc.type == "latex") {
  corrr_df %>%
    kable(digits = 2,
          booktabs = T,
          longtable = T,
          format = "latex",
          caption = "Pearson correlation coefficient between each variable within a habitat category.") %>%
    kable_styling(fixed_thead = T,
                  font_size = 10,
                  latex_options = c('repeat_header',
                                    'scale_down',
                                    'HOLD_position')) %>%
    row_spec(new_catg_rows,
             hline_after = T) %>%
    column_spec(1, width = "1in") %>%
    column_spec(c(2, 3), width = "2in")
}

if (doc.type == "html") {
  corrr_df %>%
    kable(digits = 2,
          booktabs = T,
          # longtable = T,
          caption = "Pearson correlation coefficient between each variable within a habitat category.") %>%
    kable_styling(fixed_thead = T,
                  font_size = 10,
                  latex_options = c('repeat_header',
                                    'scale_down',
                                    'HOLD_position')) %>%
    collapse_rows(columns = 1,
                  latex_hline = "major",
                  valign = "top")
}

if(doc.type == 'docx') {
  library(pander)
  panderOptions("graph.fontsize", 10)
  corrr_df %>%
    pander(digits = 2,
           caption = "(\\#tab:corr-tab)Pearson correlation coefficient between each variable within a habitat category.",
           split.tables = Inf)

### 2020-12-02 analysis/paper/appendix/appendix_s1.tex
made the font size 10 in all tables in main document and appendix

\title{Appendix S1 - \emph{Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Ecospheres}
\author{Kevin E. See\textsuperscript{1,*}, 
    \and Michael W. Ackerman\textsuperscript{1}, 
    \and Richard A. Carmichael\textsuperscript{1},
    \and Sarah L. Hoffmann\textsuperscript{1}, 
    \and Chris Beasley\textsuperscript{1}}
\date{December 01, 2020}

@@

@@

\textbf{ChannelUnit} & \textbf{Channel Unit Frequency} & \textbf{CU\_Freq} & \textbf{0.241} & \textbf{0.021} & \textbf{0.021}\\
ChannelUnit & Fast Turbulent Frequency & FstTurb\_Freq & 0.230 & 0.021 & 0.082\\
ChannelUnit & Fast NonTurbulent Frequency & FstNT\_Freq & 0.209 & 0.021 & 0.308\\
ChannelUnit & Slow Water Frequency & SlowWater\_Freq & 0.208 & 0.021 & 0.073\\
ChannelUnit & Fast Turbulent Percent & FstTurb\_Pct & 0.195 & 0.021 & 0.082\\

@@

ChannelUnit & Channel Unit Count & CU\_Ct & 0.189 & 0.021 & 0.021\\
ChannelUnit & Fast Turbulent Count & FstTurb\_Ct & 0.178 & 0.021 & 0.082\\
ChannelUnit & Slow Water Percent & SlowWater\_Pct & 0.177 & 0.021 & 0.073\\
ChannelUnit & Fast NonTurbulent Percent & FstNT\_Pct & 0.169 & 0.021 & 0.308\\
ChannelUnit & Fast NonTurbulent Count & FstNT\_Ct & 0.166 & 0.021 & 0.308\\

@@

SideChannel & Bankfull Side Channel Width & BfSCWdth & 0.223 & 0.796 & 0.796\\
SideChannel & Wetted Side Channel Width & WetSCWdth & 0.213 & 0.832 & 0.832\\

@@

SideChannel & Wetted Side Channel Percent By Area & WetSC\_Pct & 0.209 & 0.021 & 0.820\\
SideChannel & SCSm\_Freq & SCSm\_Freq & 0.153 & 0.021 & 0.921\\
SideChannel & SCSm\_Ct & SCSm\_Ct & 0.153 & 0.021 & 0.921\\
SideChannel & SC\_Area\_Pct & SC\_Area\_Pct & 0.153 & 0.021 & 0.921\\

@@

@@

>>>>

\title{Appendix S1 - \emph{Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Ecospheres}
\author{Kevin E. See\textsuperscript{1,*}, Michael W. Ackerman\textsuperscript{1}, Richard A. Carmichael\textsuperscript{1}, Sarah L. Hoffmann\textsuperscript{1}, and Chris Beasley\textsuperscript{1}}
\date{December 02, 2020}

@@

\begingroup\fontsize{10}{12}\selectfont

@@

\textbf{Channel Unit} & \textbf{Channel Unit Frequency} & \textbf{CU\_Freq} & \textbf{0.241} & \textbf{0.021} & \textbf{0.021}\\
Channel Unit & Fast Turbulent Frequency & FstTurb\_Freq & 0.230 & 0.021 & 0.082\\
Channel Unit & Fast NonTurbulent Frequency & FstNT\_Freq & 0.209 & 0.021 & 0.308\\
Channel Unit & Slow Water Frequency & SlowWater\_Freq & 0.208 & 0.021 & 0.073\\
Channel Unit & Fast Turbulent Percent & FstTurb\_Pct & 0.195 & 0.021 & 0.082\\

@@

Channel Unit & Channel Unit Count & CU\_Ct & 0.189 & 0.021 & 0.021\\
Channel Unit & Fast Turbulent Count & FstTurb\_Ct & 0.178 & 0.021 & 0.082\\
Channel Unit & Slow Water Percent & SlowWater\_Pct & 0.177 & 0.021 & 0.073\\
Channel Unit & Fast NonTurbulent Percent & FstNT\_Pct & 0.169 & 0.021 & 0.308\\
Channel Unit & Fast NonTurbulent Count & FstNT\_Ct & 0.166 & 0.021 & 0.308\\

@@

Side Channel & Bankfull Side Channel Width & BfSCWdth & 0.223 & 0.796 & 0.796\\
Side Channel & Wetted Side Channel Width & WetSCWdth & 0.213 & 0.832 & 0.832\\

@@

Side Channel & Wetted Side Channel Percent By Area & WetSC\_Pct & 0.209 & 0.021 & 0.820\\
Side Channel & SCSm\_Freq & SCSm\_Freq & 0.153 & 0.021 & 0.921\\
Side Channel & SCSm\_Ct & SCSm\_Ct & 0.153 & 0.021 & 0.921\\
Side Channel & SC\_Area\_Pct & SC\_Area\_Pct & 0.153 & 0.021 & 0.921\\

@@

\endgroup{}

\begingroup\fontsize{10}{12}\selectfont

@@

\endgroup{}
